Computing properties of independent sets by generic programming tensor networks \thanks{\funding{...}}

### 2022-04-11 paper/paper.tex

The source code in Julia language for this paper can be found in the Github repository~\cite{GraphTensorNetworks}. 
There is a short introduction to this repository as well a gist to show how it works in Appendix~\ref{sec:technical}.
We expect our tool can be used to understand and study many interesting applications of independent sets and beyond.
We also hope the toolkit we built, including tensor network contraction order optimization and efficient tropical matrix multiplication, can be helpful to the development of other scientific software.

@@

This appendix covers some technical guides for productivity, including an introduction to an open-source package \href{https://github.com/QuEraComputing/GraphTensorNetworks.jl}{GraphTensorNetworks}~\cite{GraphTensorNetworks} implementing the algorithms in this paper and the gist about how this package is implemented.
One can install \texttt{GraphTensorNetworks} a Julia REPL, by first type \colorbox{lightgray}{\texttt{]}} to enter the \texttt{pkg>} mode and then type
\begin{lstlisting}
pkg> add GraphTensorNetworks
\end{lstlisting}
followed by an \colorbox{lightgray}{\texttt{<ENTER>}} key.
To use it for solving solution space properties, just go back to the normal mode (type \colorbox{lightgray}{\texttt{<BACKSPACE>}}) and type

\begin{lstlisting}
julia> using GraphTensorNetworks, Graphs

@@

Here the main function \texttt{solve} takes three inputs, the problem instance of type \texttt{IndependentSet}, the property instance of type \texttt{GraphPolynomial} and an optional key word argument \texttt{usecuda} to decide use GPU or not.
If one wants to use GPU to accelerate the computation, ``\texttt{using CUDA}'' must be uncommented.
The problem instance takes four arguments to initialize, the only positional argument is the graph instance one wants to solve, the keyword argument \texttt{optimizer} is for specifying the tensor network optimization algorithm, the keyword argument \texttt{weights} is for specifying the weights of vertices as either a vector or \texttt{NoWeight()} and the keyword argument \texttt{openvertices} is for specifying the degrees of freedom not summed over.
Here, we use \texttt{TreeSA} method as the tensor network optimizer, and leave \texttt{weights} and \texttt{openvertices} the default values. The \texttt{TreeSA} algorithm, which was invented in Ref.~\cite{Kalachev2021}, performs the best in most of our applications.
The first execution of this function will be a bit slow due to Julia's just-in-time compiling.
After that, the subsequent runs will be fast.
The following diagram lists possible combinations of input arguments, where functions in the \texttt{Graph} are mainly defined in package \texttt{Graphs}, and the rest can be found in \texttt{GraphTensorNetworks}.

@@

They can be installed in a similar way to \texttt{GraphTensorNetworks}.
After installing the required packages, one can open a Julia REPL, and copy-paste the following code snippet into it.

>>>>

The source code in Julia language for this paper can be found in our Github repository~\cite{GenericTensorNetworks}. 
There is a short introduction to this repository as well a gist to show how it works in Appendix~\ref{sec:technical}.
We expect our tool can be used to understand and study many interesting applications of independent sets and beyond.
We also hope the toolkit we built, including tensor network contraction order optimization and efficient tropical matrix multiplication, can be helpful to the development of other scientific software.

@@

This appendix covers some technical guides for productivity, including an introduction to an open-source package \href{https://github.com/QuEraComputing/GenericTensorNetworks.jl}{GenericTensorNetworks}~\cite{GenericTensorNetworks} implementing the algorithms in this paper and the gist about how this package is implemented.
One can install \texttt{GenericTensorNetworks} a Julia REPL, by first type \colorbox{lightgray}{\texttt{]}} to enter the \texttt{pkg>} mode and then type
\begin{lstlisting}
pkg> add GenericTensorNetworks
\end{lstlisting}
followed by an \colorbox{lightgray}{\texttt{<ENTER>}} key.
To use it for solving solution space properties, just go back to the normal mode (type \colorbox{lightgray}{\texttt{<BACKSPACE>}}) and type

\begin{lstlisting}
julia> using GenericTensorNetworks, Graphs

@@

Here the main function \texttt{solve} takes three inputs, the problem instance of type \texttt{IndependentSet}, the property instance of type \texttt{GraphPolynomial} and an optional key word argument \texttt{usecuda} to decide use GPU or not.
If one wants to use GPU to accelerate the computation, ``\texttt{using CUDA}'' must be uncommented.
The problem instance takes four arguments to initialize, the only positional argument is the graph instance one wants to solve, the keyword argument \texttt{optimizer} is for specifying the tensor network optimization algorithm, the keyword argument \texttt{weights} is for specifying the weights of vertices as either a vector or \texttt{NoWeight()} and the keyword argument \texttt{openvertices} is for specifying the degrees of freedom not summed over.
Here, we use \texttt{TreeSA} method as the tensor network optimizer, and leave \texttt{weights} and \texttt{openvertices} the default values. The \texttt{TreeSA} algorithm, which was invented in Ref.~\cite{Kalachev2021}, performs the best in most of our applications.
The first execution of this function will be a bit slow due to Julia's just-in-time compiling.
After that, the subsequent runs will be fast.
The following diagram lists possible combinations of input arguments, where functions in the \texttt{Graph} are mainly defined in package \texttt{Graphs}, and the rest can be found in \texttt{GenericTensorNetworks}.

@@

They can be installed in a similar way to \texttt{GenericTensorNetworks}.
After installing the required packages, one can open a Julia REPL, and copy-paste the following code snippet into it.

### 2022-04-11 paper/paper_before_maddie.tex

\begin{description}
	\item[\href{https://github.com/under-Peter/OMEinsum.jl}{OMEinsum} and \href{https://github.com/Happy-Diode/OMEinsumContractionOrders.jl}{OMEinsumContractionOrders}] are packages providing the support for Einstein's (or tensor network) notation and contraction order optimizations.
    \texttt{OMEinsumContractionOrders} implements state-of-the-art algorithms for finding the optimal contraction order for a tensor network, including the KaHypar+Greedy~\cite{Gray2021, Pan2021} and local transformation based approaches~\cite{Kalachev2021},
	\item[\href{https://github.com/TensorBFS/TropicalNumbers.jl}{TropicalNumbers} and \href{https://github.com/TensorBFS/TropicalGEMM.jl}{TropicalGEMM}] are packages providing tropical number and efficient tropical matrix multiplication,
	\item[\href{https://github.com/JuliaGraphs/Graphs.jl}{Graphs}] is a package providing graph utilities, like random regular graph generator,
	\item[\href{https://github.com/JuliaMath/Polynomials.jl}{Polynomials}] is a package providing polynomial algebra and polynomial fitting,
	\item[\href{https://github.com/scheinerman/Mods.jl}{Mods} and \href{https://github.com/JuliaMath/Primes.jl}{Primes}] are packages providing finite field algebra and prime number generations.
\end{description}

@@

For better performance, we recommend checking our GitHub repository for the full featured version:
\href{https://github.com/Happy-Diode/GenericTensorNetworks.jl}{https://github.com/Happy-Diode/GenericTensorNetworks.jl}.
It can be installed in a similar style to other packages.

>>>>

\begin{description}
	\item[\href{https://github.com/under-Peter/OMEinsum.jl}{OMEinsum} and \href{https://github.com/QuEraComputing/OMEinsumContractionOrders.jl}{OMEinsumContractionOrders}] are packages providing the support for Einstein's (or tensor network) notation and contraction order optimizations.
    \texttt{OMEinsumContractionOrders} implements state-of-the-art algorithms for finding the optimal contraction order for a tensor network, including the KaHypar+Greedy~\cite{Gray2021, Pan2021} and local transformation based approaches~\cite{Kalachev2021},
	\item[\href{https://github.com/TensorBFS/TropicalNumbers.jl}{TropicalNumbers} and \href{https://github.com/TensorBFS/TropicalGEMM.jl}{TropicalGEMM}] are packages providing tropical number and efficient tropical matrix multiplication,
	\item[\href{https://github.com/JuliaGraphs/Graphs.jl}{Graphs}] is a package providing graph utilities, like random regular graph generator,
	\item[\href{https://github.com/JuliaMath/Polynomials.jl}{Polynomials}] is a package providing polynomial algebra and polynomial fitting,
	\item[\href{https://github.com/scheinerman/Mods.jl}{Mods} and \href{https://github.com/JuliaMath/Primes.jl}{Primes}] are packages providing finite field algebra and prime number generations.
\end{description}

@@

For better performance, we recommend checking our GitHub repository for the full featured version:
\href{https://github.com/QuEraComputing/GenericTensorNetworks.jl}{https://github.com/QuEraComputing/GenericTensorNetworks.jl}.
It can be installed in a similar style to other packages.
